Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting \textcolor{red}{plus court} : Simple and robust inference of connectomes using partial correlation coefficients ?

### 2014-06-06 article.tex
fix to compil

\title[Connectomics challenge]{Inferring neural networks from fluorescent
                               calcium imaging using partial correlation and
                               sample weighting \textcolor{red}{plus court}}

Simple and robust inference of connectomes using partial correlation coefficients

%% 
Discovery/Infering/Retrieving/... connectomes 
Robust
Using partial correlation
[from calcium imaging]

\textcolor{red}{Discussion on the order of the partial correlation}

@@

% Discussion on the metrics?

>>>>

\title[Connectomics challenge]{Inferring neural networks from fluorescent
                               calcium imaging using partial correlation and
                               sample weighting \textcolor{red}{plus court} : Simple and robust inference of connectomes using partial correlation coefficients
?}

% %% 
% Discovery/Infering/Retrieving/... connectomes 
% Robust
% Using partial correlation
% [from calcium imaging]

@@

% Discussion on the metrics?
%\textcolor{red}{Discussion on the order of the partial correlation}
